What is disputed on the web?

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Fleshing out the paper. We now have some rough text for every section except the bits on what one can use this data for, and an exploration of the date itself

\documentclass{acm_proc_article-sp}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\newcommand{\want}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\node}[1]{}

@@

In this paper we describe a method for automatically aquiring a corpus of disputed claims from the web. By {\it disputed claim} we mean a statement about the world that some sources believe are true, and other sources believe is false. Our intention is that this corpus of disputed claims will be used as input to tools that help users know what information they encounter in their lives is potentially unreliable.

We identify disputed claims by searching the web for patterns that indicate that a particular phrase is a disputed claim. One such pattern is ``the misconception that $S$'', an instance of which would be ``the minconception that {\it the moon is made of cheese}''. If we find a document that contains this text then that suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.

We have found many other patterns that have this property, some of which we list in Figure~\ref{templates}. Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{hearst-hyponyms} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.

@@

We believe that our corpus is the first large-scale corpus of disputed claims.

@@

@@

We distinguish between a {\it contradiction} and a {\it dispute}. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong. For example the text ``only idiots think that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''. A {\it contradiction} is logical, while a {\it dispute} is social. It is possible to have a contradiction without a dispute and a dispute without a contradiction. While the concepts are different, they are obviously closely related. Usually if someone disputes a claim it is because they believe an alternative claim that contradicts it.

We distinguish between a claim that is {\it contradicted} and a claim that is {\it disputed}. 
A claim in a document is {\it contradicted} if there is another document somewhere else that makes a contradictory claim. A claim is {\it disputed} if another document explicitly says

A claim is {\it disputed} if another document

For example if one document says ``The moon is made of cheese'' and another document says ``The moon is made of rock'' then then the first statement is contradicted by the first.

We consider a claim to be disputed if at least one source suggests that the claim is true, and at least one source suggests that the claim is not true.

One way to find disputed claims is to compare statements on different web pages and look for contradictions. AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a {\it functional} verb maps the same subject to multiple different objects and the difference cannot be resolved using a semantic knowledge.

Harabagiu et al\cite{Harabagiu2006}

\x{A contradiction is not the same as a dispute. A contradiction is where the information is different. A dispute is where the different parties BELIEVE the disagree. }

The RTE-3 Recognizing Textual entailment task

This turned out to be a hard problem;

scanning 117 million web pages yielded only 110 genuine contradictions.

\todo{We might want to try using TextRunner ourselves.}

and then infers a contradiction when

infers which verbs should have like functions, and then reports a contradiction when different statements infer that a verb maps a subject to a different object. The authors found that approximately 99\% of the apparent contradictions that they found were not genuine contradictions, and that it would require domain knowledge to understand why.

\x{Need to talk about Harabagiu et al 2006 about contradiction detection through negation.}
\x{Need to talk about three-way RTE task}.

always map the subject to the same object, and then reports a contradiction when different statements

In theory, one could find disputed claims by comparing statements on different web pages and looking for contradictions.

However the problem of detecting contradictions has been found to be very difficult in practice~\cite{contradiction-hard}. Does ``

\todo{Need to give a good citation of why contradiction detection is hard.}

We consider a claim to be disputed if at least one author both believes that the claim is false and believes that

In theory, the best way to find disputed claims would be to find places where two documents make statements that contradict each other. However this problem has been found to be very difficult in practice~\cite{contradiction-hard}.

We obtain such statements $S$ by using the Yahoo BOSS search API to search for strings such as ``the misconception that''. We then parse the text that follows using a natural language parser and discard any text that either does not appear to be a valid statement, or that includes referents such as ``it'' or ``he'' that would otherwise need to be resolved based on the context.

\subsection{Disputed Templates}

\x{We use Yahoo BOSS.}
\x{Yahoo BOSS limits us to 1000 results per query.}
\x{We use dates to target pages that were published on a particular date.}
\x{We have not yet done a details analysis of what proportion of pages were actually written on this date}
\todo{Analyse how well our date targetting works}

\x{We have a database of XXX different text strings, some of which may be the same claim.}

\begin{figure}[tb]
  \begin{tabular}{|ll|}
    \hline
    {\bf Google Count\footnotemark} & {\bf Template}\\ 
    \hline
    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
    163,000,000 & believe that \\
    206,000,000 & think that \\
    49,500,000 & idea that \\
    33,600,000 & claim that \\
    \hline
    \multicolumn{2}{|c|}{\it Something others believe}\\
    120,000,000 & the belief that \\
    49,000,000 & who believe that \\
    50,500,000 & who think that \\
    10,100,000 & believing that \\
    9,430,000 & claiming that \\
    \hline
    \multicolumn{2}{|c|}{\it Something false}\\
    243,000,000 & it is not the case that \\
    30,700,000 & it is not true that \\
    15,600,000 & the misconception that \\
    13,000,000 & the delusion that \\
    12,400,000 & the myth that \\
    9,960,000 & into believing that \\
    7,190,000 & the mistaken belief that \\
    4,950,000 & the fallacy that \\
    3,720,000 & the lie that \\
    3,700,000 & mistaken belief that \\
    3,600,000 & the false belief that \\
    3,440,000 & the deceit that \\
    2,140,000 & the deception that \\
    1,760,000 & the misunderstanding that \\
    1,630,000 & mistakenly believe that \\
    1,090,000 & false claim is that \\
    1,290,000 & the hoax that \\
    698,000 & absurdity of the claim that \\
    681,000 & falsely claimed that \\
    659,000 & no longer think that \\
    654,000 & urban legend that \\
    530,000 & the absurd idea that \\
    373,000 & erroneously believe that \\
    334,000 & the fabrication that \\
    103,000 & falsely claiming that \\
    140,000 & erroneous belief that \\
    72,600 & falsely claim that \\
    152,000 & bogus claim that \\
    224,000 & the fantasy that \\
    171,000 & incorrectly claim that \\
    249,000 & incorrectly claimed that \\
    232,000 & incorrectly believe that \\
    98,900 & stupidly believe that \\
    429,000 & falsely believe that \\
    376,000 & wrongly believe that \\
    189,000 & falsely suggests that \\
    280,000 & falsely claims that \\
    148,000 & false claim that \\
    136,000 & no longer believe that \\
    65,300 & urban myth that \\
    59,500 & falsely stated that \\
    \hline
  \end{tabular}
  \label{templates}
  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}

@@

\x{Some prefixes suggest that some disagree, without saying that they do. E.g. ``people who believe that''}

\x{Include a table with templates we use and templates we generated}

\subsection{Selecting Good Statements}

@@

\subsection{Generating New Templates}

\x{Following the distributional hypothesis.}
\x{Search for known disputed claims and find most frequent words that surround them.}

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\newcommand{\want}[1]{}
\newcommand{\idea}[1]{}
\newcommand{\note}[1]{}

@@

In this paper we describe a method for automatically aquiring a corpus of disputed claims from the web. We consider a claim to be {\it disputed} if some people believe both that others are making the claim, and that the claim is not true.

We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$''. For example, if a document contains the text ``the minconception that {\it the moon is made of cheese}'', this suggests that the author of the document believes both that the statement ``{\it the moon is made of cheese}'' is false, and that there are other authors who claim that ``{\it the moon is made of cheese}'' is true.

We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}. Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{hearst-hyponyms} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.

@@

We believe that ours is the first attempt to automatically aquire a corpus of disputed claims.

@@

The problem of detecting disputed claims is closely related to the well studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''.
A claim $H$ is {\it disputed} if a document somewhere on the web suggests both that some people are claiming $H$ and that those people are wrong. For example the text ``we disagree with the assertion that the moon is made of cheese'' {\it disputes the claim} ``the moon is made of cheese''. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that their is a contradiction between their beliefs.

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonoby of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction. AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{rte-3} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

Detecting contradictions has proven to be a hard problem. Much of the difficulty comes from the fact that it typically requires deep semantic knowledge to determine whether two statements that look like they might be contradictory actually are. ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important. The advantage of looking for disputes rather than contradictions is that is is much easier - humans do the hard work of identifying contradictions and deciding whether they are important. The disadvantage of looking for disputes is that this method will only identify contradictions that humans have already identified.

@@

\x{Include a diagram showing the stages of our dispute finding process}
\maybe{Talk about theories of contrast???}
\maybe{Look at Kehler 2002 on CONTRAST???}

Figure~\ref{not-yet} shows the process we use to build our corpus of disputed claims. 
We find disputed claims by searching the web for for patterns like ``the misconception that $S$'' and ``it is not the case that $S$'' (Section~\ref{searchpattern}). 
For every page that contains the pattern, we grab the raw text from the end of the prefix string, up until the end end of the sentence. We then pass each such block of text to a parser that discards any text that does not appear to be a statement (Section~\ref{filterclaim}).

Given a set of known disputed claims, we then go back and generate new patterns by searching for those claims on the web and looking for contexts in which those claims often appear.

\subsection{Searching for Patterns}
\label{searchpattern}

We search the web for patterns that indicate that a claim is disputed. Figure~\ref{templates} shows a subset of the patterns that we search for. For each pattern, we show the number of times that Google estimates that the pattern appears on the web.

Rather than building our own search engine, we use the Yahoo BOSS search API~\cite{yahoo-boss} to search for patterns. We search Yahoo BOSS for a raw string such as ``the misconception that'' and then download every web page that Yahoo lists in its search results.

We form a {\it candidate claim} by taking all text from the end of the prefix we searched for, up to the nearest sentence-ending punctuation character or HTML tag (e.g. '.','?','!',\texttt{</p>},\texttt{</h1>}, etc).

We want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages. The Yahoo BOSS API does not offer the ability to request only pages updated in a given date range. We thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}. We instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, and some web pages either don't include the date the article was posted, or write their date in a different format. Indeed our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).

\todo{Produce some kind of measure of how well date searching actually works}

Another advantage of including the date in the search query is it reduces the impact of Yahoo's limit of only 1000 results per query. Since we include the date in the query, this translates into a limit of only 1000 results per pattern per day, which gives us access to a much larger set of pages.

Since we are using an existing search engine, we are limited to searching for simple text strings. This leads us to generate multiple patterns that are almost the same, other than for synonyms. E.g. ``the lie that'' vs ``the deceipt that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence. While we could do the search anyway, and then filter out all pages in which the parts were not in the same sentence, it would be inefficient, since many pages would not contain the pattern.

In the longer term we would like to have a more elegant search infrastructure, but for the time being this approach seems to work reasonably well.

\subsection{Generating Patterns}
\label{newtemplate}

Figure~\ref{templates} shows some of the patterns that we search for.

As the figure shows, not all patterns have exactly the same meaning. We divide patterns into three fuzzily-grouped categories:

\begin{itemize}
 \item {\bf False:} The author believes the claim is wrong
 \item {\bf Believed by others:} The author believes others think this, and it is likely that the author disagrees. Further inspection is required to determine whether the author disagrees with the claim. 
 \item {\bf Could be challenged:} The author feels the need to state that someone believes something, which suggests that this is something that one might not believe. For example, if an author says ``I think America is a great place'' this doesn't suggest that the claim is false, but the mere fact that they declared that they thought that suggests that they are aware that the claim could be challenged.
\end{itemize}

We grouped patterns into categories by hand, based on a brief inspection of pages that were using each of the patterns.

Which patterns one should use depends on what one wishes to use the resulting corpus of disputed claims for. If one wants to only have claims for which we can present web pages that argue that the claim is false, then only the first set of patterns should be used. If however one just wishes to see what things people think are worthy of having opinions expressed about, then the full set is useful.

We started with an initial set of patterns that we wrote by hand. We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim. From this set of candidate prefix patterns, we manually selected patterns that we believed would lead us, as a human, to infer that the author thought the claim was disputed, believed by others, or open to challenge.

\todo{Give some stats about our patterns}
\todo{Use Yahoo BOSS counts rather than Google}
\note{It seems silly to use Google's counts for these when we are using Yahoo BOSS. Someone should write a script to re-generate this table using Yahoo BOSS counts.}

\todo{Analyse how well our date targetting works}

\begin{figure}[tb]
  \begin{tabular}{|ll|}
    \hline
    {\bf Google Count\footnotemark} & {\bf Template}\\ 
    \hline
    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
    163,000,000 & believe that \\
    206,000,000 & think that \\
    49,500,000 & idea that \\
    33,600,000 & claim that \\
   \hline
   \multicolumn{2}{|c|}{\it Something others believe}\\
    120,000,000 & the belief that \\
    49,000,000 & who believe that \\
    50,500,000 & who think that \\
    10,100,000 & believing that \\
    9,430,000 & claiming that \\
    \hline
    \multicolumn{2}{|c|}{\it Something false}\\
    243,000,000 & it is not the case that \\
    30,700,000 & it is not true that \\
    15,600,000 & the misconception that \\
    13,000,000 & the delusion that \\
    12,400,000 & the myth that \\
    9,960,000 & into believing that \\
    8,970,000 & disagree with the claim that \\
    7,190,000 & the mistaken belief that \\
    6,160,000 & disagree with the assertion that \\
    4,950,000 & the fallacy that \\
    3,720,000 & the lie that \\
    3,700,000 & mistaken belief that \\
    3,600,000 & the false belief that \\
    3,440,000 & the deceit that \\
    2,290,000 & cast doubt on the claim that \\
    2,140,000 & the deception that \\
    1,760,000 & the misunderstanding that \\
    1,630,000 & mistakenly believe that \\
    1,090,000 & false claim is that \\
    1,290,000 & the hoax that \\
    698,000 & absurdity of the claim that \\
    681,000 & falsely claimed that \\
    659,000 & no longer think that \\
%     654,000 & urban legend that \\
%     530,000 & the absurd idea that \\
%     373,000 & erroneously believe that \\
%     334,000 & the fabrication that \\
%     103,000 & falsely claiming that \\
%     140,000 & erroneous belief that \\
%     72,600 & falsely claim that \\
%     152,000 & bogus claim that \\
%     224,000 & the fantasy that \\
%     171,000 & incorrectly claim that \\
%     249,000 & incorrectly claimed that \\
%     232,000 & incorrectly believe that \\
%     98,900 & stupidly believe that \\
%     429,000 & falsely believe that \\
%     376,000 & wrongly believe that \\
%     189,000 & falsely suggests that \\
%     280,000 & falsely claims that \\
%     148,000 & false claim that \\
%     136,000 & no longer believe that \\
%     65,300 & urban myth that \\
%     59,500 & falsely stated that \\
    \hline
  \end{tabular}
  \label{templates}
  \caption{Some of the templates that we use to search for disputed claims, and Google's rough estimate of how many times each one appears on the web}

@@

\subsection{Filtering Statements}
\label{filterclaim}

We pass each such chunk of raw text to a natural language parser (custom grammar, and an NLTK~\cite{nltk} regexp parser). We throw away any chunk of text that does not appear to be a statement, or which uses a referent (such as ``it'' or ``he'') that cannot be easily resolved. Figure~\ref{filtered} shows examples of phrases that we filter.

\begin{figure*}[t]
\begin{tabular}{|l|l|l|}
  \hline
  {\bf extracted text} & {\bf accepted} & {\bf reason} \\
  \hline
  {\it the false claim that} won't go away & reject & ``wont go away'' is not a statement \\
  {\it falsely claimed that} he didn't do it & reject & ``he'' and ``it'' are unbound referents \\ 
  {\it wrongly believe that} the moon is made of cheese & accept & \\
  {\it false claim that} Elvis is alive despite all evidence & \\
  \hline
\end{tabular}
\label{filtered}
\caption{We filter out text that does not look like a statement}

\end{figure*}

\todo{Our parser is currently a bit rubbish. Need to work out how to do this properly.}
\todo{We need to use the correct terminology here.}

@@
